The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-18 src/ms.tex
more tweaks to author list formatting

\documentclass[modern]{aastex631}
\usepackage{xspace}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{ulem}

@@

\submitjournal{ApJ}

@@

\author{Astropy Collaboration}
\noaffiliation
{\let\thefootnote\relax\footnote{{The author list has two parts: the authors that made significant contributions to the writing of the paper in order of contribution, followed by contributors to the \astropy Project in alphabetical order. \textbf{The position in the author list does not correspond to contributions to the \astropy Project as a whole.} A more complete list of contributors to the core package can be found in the \href{https://github.com/astropy/astropy/graphs/contributors}{package repository}, and at the \href{http://www.astropy.org/team.html}{\astropy team webpage}.}}}

% \input{author.tex}

@@

\keywords{%
    Astrophysics - Instrumentation and Methods for Astrophysics
    ---
    methods: data analysis
    ---
    methods: miscellaneous
}

@@

\begin{figure}[th]
    \begin{centering}
      \includegraphics[width=\textwidth]{python-mentions.pdf}
        \caption{
            Yearly full-text mentions of programming languages (indicated in the
            figure legend) in refereed publications in the astronomical
            literature database in the Astrophysics Data System (ADS).
            \python has rapidly become the dominant programming language
            mentioned in refereed articles over the last 10 years.
        }
        \label{fig:python-mentions}
    \end{centering}
\end{figure}

>>>>

\documentclass[modern]{aastex631}
\NewPageAfterKeywords
\usepackage{xspace}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{ulem}

@@

% \submitjournal{ApJ}

@@

\author{Astropy~Collaboration}
\noaffiliation
{\let\thefootnote\relax\footnote{{
  The author list has two parts: the authors that made significant contributions
  to the writing and/or coordination of the paper (in order of contribution),
  followed by maintainers of and contributors to to the Astropy Project (in
  alphabetical order). \textbf{The position in the author list does not
  correspond to contributions to the Astropy Project as a whole.} A more
  complete list of contributors to the core package can be found in the
  \href{https://github.com/astropy/astropy/graphs/contributors}{package
  repository}, and at the \href{http://www.astropy.org/team.html}{Astropy team
  webpage}.
}}}

\input{static/authors.tex}

@@

% \keywords{%
%     Astrophysics - Instrumentation and Methods for Astrophysics
%     ---
%     methods: data analysis
%     ---
%     methods: miscellaneous
% }

@@

\begin{figure}[t!]
    \begin{centering}
      \includegraphics[width=\textwidth]{python-mentions.pdf}
        \caption{
            Yearly full-text mentions of programming languages (indicated in the
            figure legend) in refereed publications in the astronomical
            literature database in the Astrophysics Data System (ADS).
            \python has rapidly become the dominant programming language
            mentioned in refereed articles over the last 10 years.
        }
        \label{fig:python-mentions}
    \end{centering}
\end{figure}
